\documentclass[10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{array}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{hyperref}

\title{HFT-FPGA CDC Architecture Note}
\author{}
\date{\today}

\begin{document}
\maketitle

\section*{Purpose}
This note summarizes the clock-domain organization for the CDC-enabled wrappers in the RTL. The original protocol cores remain single-clock reference implementations, while wrapper modules add safe stream crossing with reusable CDC primitives.

\section*{CDC Building Blocks}
\begin{itemize}
    \item \textbf{async\_fifo.sv}: Dual-clock FIFO using Gray-coded pointers and synchronizer stages for pointer crossing.
    \item \textbf{cdc\_level\_sync.sv}: Multi-flop synchronizer for stable single-bit levels.
    \item \textbf{cdc\_pulse\_sync.sv}: Toggle/ack based pulse transfer for one-shot events.
\end{itemize}

\section*{Wrapper Domain Map}
\subsection*{tcp\_send\_framer\_cdc.sv}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.22\linewidth} >{\raggedright\arraybackslash}p{0.20\linewidth} >{\raggedright\arraybackslash}p{0.50\linewidth}}
\toprule
\textbf{Signal Group} & \textbf{Domain} & \textbf{Notes} \\
\midrule
\endhead
Control in (\texttt{start}, \texttt{payload\_length}) & \texttt{in\_clk} & Drives the single-clock core instance. \\
Payload in (\texttt{in\_valid/data/sop/eop/error}) & \texttt{in\_clk} & Consumed by \texttt{tcp\_send\_framer}. \\
Core stream out (\texttt{core\_out\_*}) & \texttt{in\_clk} & Packed into FIFO write data. \\
FIFO read stream (\texttt{out\_valid/data/sop/eop/error}) & \texttt{out\_clk} & Unpacked from FIFO read side. \\
\texttt{busy} output & \texttt{out\_clk} & Busy level synchronized from core plus FIFO occupancy indication. \\
\texttt{done} output & \texttt{out\_clk} & Reconstructed as a pulse on final output beat transfer. \\
\bottomrule
\end{longtable}

\subsection*{tcp\_receive\_parser\_cdc.sv}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.22\linewidth} >{\raggedright\arraybackslash}p{0.20\linewidth} >{\raggedright\arraybackslash}p{0.50\linewidth}}
\toprule
\textbf{Signal Group} & \textbf{Domain} & \textbf{Notes} \\
\midrule
\endhead
Input stream (\texttt{in\_valid/data/sop/eop/error}) & \texttt{in\_clk} & Parsed by \texttt{tcp\_receive\_parser} core. \\
Parsed payload out (\texttt{out\_valid/data/sop/eop}) & \texttt{out\_clk} & Crossed via async FIFO. \\
Metadata (\texttt{message\_valid/error/length}) & \texttt{in\_clk} & Exposed directly from core domain in current wrapper. \\
\bottomrule
\end{longtable}

\subsection*{udp\_receive\_parser\_cdc.sv}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.22\linewidth} >{\raggedright\arraybackslash}p{0.20\linewidth} >{\raggedright\arraybackslash}p{0.50\linewidth}}
\toprule
\textbf{Signal Group} & \textbf{Domain} & \textbf{Notes} \\
\midrule
\endhead
Input stream (\texttt{in\_valid/data/sop/eop/error}) & \texttt{in\_clk} & Parsed by \texttt{udp\_receive\_parser} core. \\
Payload out (\texttt{out\_valid/data/sop/eop}) & \texttt{out\_clk} & Crossed via async FIFO. \\
Header/status metadata (\texttt{src\_port}, \texttt{dst\_port}, \texttt{udp\_length}, \texttt{payload\_length}, \texttt{packet\_valid/error}) & \texttt{in\_clk} & Exposed directly from core domain in current wrapper. \\
\bottomrule
\end{longtable}

\section*{Integration Guidance}
\begin{itemize}
    \item Treat parser metadata in wrappers as \texttt{in\_clk}-domain outputs unless explicit synchronizers are added.
    \item Consume wrapper stream outputs in \texttt{out\_clk} domain only.
    \item Keep CDC crossing centralized in shared primitives to avoid ad-hoc per-module CDC logic.
\end{itemize}

\section*{Verification Notes}
Current testbench split:
\begin{itemize}
    \item Single-clock golden tests for core protocol modules.
    \item CDC primitive tests for FIFO and synchronizers.
    \item CDC wrapper tests for cross-clock stream behavior.
\end{itemize}

\end{document}
